---
title: "Jarad Niemi"
pagetitle: "Jarad Niemi"
image: assets/headshot.svg
image-alt: "Jarad Niemi"
about:
  id: hero
  template: trestles
  image-shape: round
  image-width: 13em
  links:
    - icon: envelope
      text: Email
      href: mailto:niemi@iastate.edu
    - icon: file-earmark-text
      text: CV
      href: https://github.com/jarad/cv/raw/master/JaradNiemi-CV.pdf
    - icon: github
      text: GitHub
      href: https://github.com/jarad
    - icon: person-badge
      text: ORCID
      href: https://orcid.org/0000-0002-5079-158X
    - icon: mortarboard
      text: Scholar
      href: https://scholar.google.com/citations?user=sRLc6F8AAAAJ&hl=en
    - icon: linkedin
      text: LinkedIn
      href: https://www.linkedin.com/in/jaradniemi
---

```{r}
source("R/site.R")
pos = cv("positions")
pos = pos[is.na(pos$end_date) & pos$institution == "Iowa State University", ]
```

::: {#hero}

::: {.lead-in}
`r paste(paste(pos$title, pos$unit, sep = ", "), collapse = " &middot; ")`<br>
Iowa State University
:::

I am a professor in the [Department of Statistics](https://www.stat.iastate.edu/)
at Iowa State University and director of its
[Data Science Program](https://datascience.iastate.edu/).
My research focuses on Bayesian inference and the computational methods that make it
practical, such as Markov chain Monte Carlo and sequential Monte Carlo,
with applications in disease forecasting, agriculture and the environment.

:::

## News

```{r}
#| output: asis
n = news(6)
emit('<ul class="news">',
     paste0('<li><span class="when">', h(n$shown), '</span><span>', n$html, '</span></li>', collapse = ""),
     '</ul>')
```

```{r}
#| output: asis
now = current_courses()
if (nrow(now)) {
  t = term_of()
  emit('<h2>Teaching in ', t$term, ' ', t$year, '</h2><ul class="course-cards">',
       paste0('<li class="course-card"><div class="course-number">', link(h(now$number), now$url),
              '</div><div class="course-title">', txt(now$title), '</div></li>', collapse = ""),
       '</ul>')
}
```

## Contact

Department of Statistics, 2103 Snedecor Hall, Iowa State University, Ames, IA 50011-1210<br>
<niemi@iastate.edu> &middot; (515) 294-8679
